NLIZE: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-23 paper/task.tex
update tasks

\section{Task Analysis}
\label{sec:task}
Effective identify and itemize the visualization tasks and the corresponding goal is the first step in designing a useful visual representation.

>>>>

\section{Task Analysis}
\label{sec:task}
Identify the analysis goals and distill the corresponding visualization tasks is the first yet significant step in designing a useful tool. In this section, we examine how domain experts approach the challenge of analyzing a new model and assess its strength and weakness.
Then, we reify the observations into a common paradigm and identify where and how a visualization tool could help experts intrepret the model and development intuitve, more importantly, how such augmentation fit into the domain experts' though process and workflow.

During our long-term colloration with two domain experts in NLP, we have conducted extensive interview and discussion on the common approach researchers employ to interpret the behavior and obtain intuition for a new model.
%
Often, the most important metric for evaluating a model is the prediction accuracy. However, most researchers would agree, the accuracy alone does not provide the full picture. The model could perform much worse on a different test set. The model may prodcue many correct predictions for the ``wrong'' reasons (e.g., pickup unintended pattern in the training data that does not exist in real word senarios).
%
As a result, NLP researchers often employ a set of tests, which are driven by their domain knowledge and hypotheses based on the archtecture, to assess the model.
%
A stereotypical senario can be summarized as the follow.
%
To assess a model for a specific NLP task, the research start the analysis from looking at the failure cases.

\shusen{What is the paradigm?}
Look at example, perturb the example, see how the perturb the one fails,

learn the limtation and strength from the where and how the errors occurs. iterate

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{errorAnalysis}
 \caption{How domain experts carry out error analysis on the model.}
\label{fig:modelPipeline}
\end{figure}
